\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage[UTF8,fontset=none]{ctex}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{pgfornament}
\usepackage{setspace}
\usepackage{fancyhdr}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.8\baselineskip}
\onehalfspacing

\setCJKmainfont{Songti SC}
\setCJKsansfont{Heiti SC}
\setCJKmonofont{Heiti SC}
\newCJKfontfamily\kaishu{Heiti SC}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{%
  \ifnum\value{page}=1 220%
  \else\ifnum\value{page}=2 284%
  \else\thepage%
  \fi\fi
}
\renewcommand{\headrulewidth}{0pt}

\definecolor{ink}{HTML}{2B2B2B}
\definecolor{accent}{HTML}{6B1F2B}
\pagecolor{white}
\color{ink}

% Decorative rules (no external assets)
\newcommand{\ornamentrule}{%
  \par\noindent
  \begin{center}
    \color{accent}\pgfornament[width=0.72\linewidth]{88}
  \end{center}
  \par
}

\newcommand{\lettertitle}[1]{%
  \begin{center}
    \vspace*{0.5em}
    {\color{accent}\pgfornament[width=0.55\linewidth]{75}\par}
    \vspace{0.6em}
    {\Large\bfseries #1\par}
    \vspace{0.6em}
    {\color{accent}\pgfornament[width=0.55\linewidth]{75}\par}
  \end{center}
  \vspace{0.6em}
}

\begin{document}

\lettertitle{致文珺}

\begin{flushright}
{\color{accent}\kaishu 死生契阔，与子成说。执子之手，与子偕老。——《诗经·邶风·击鼓》}
\end{flushright}

\ornamentrule

{\kaishu My dearest \emph{[Her Name]},}

中文

I have been trying to find the right words for something that has become wonderfully simple in my heart: I love you. Not as an idea, not as a moment, but as a steady truth I return to---in ordinary mornings, in quiet evenings, and in every small space between.

You have a grace that changes the atmosphere of a room. When life is loud, you bring calm; when it is heavy, you bring lightness; when it is uncertain, you bring a kind of courage that feels like home. I admire the way you care, the way you notice, the way you make beauty out of what others might overlook.

If I could give you one gift in return for all you are, it would be this: the certainty that you are cherished. Not only for what you do, but for who you are---your laughter, your tenderness, your strength, your mind, your patience, and even the soft, honest edges that make you human and real.

Thank you for building a life with me. Thank you for the thousand unseen kindnesses, for the forgiveness you offer, for the dreams you keep, for the love you practice like an art. I am proud to be your husband. I am grateful to be your friend. And I would choose you again, in any lifetime, in any version of the world.

\ornamentrule

\begin{flushright}
With all my love,\\[0.5em]
{\Large\kaishu [Your Name]}
\end{flushright}

\vfill
\begin{center}
{\color{accent}\pgfornament[width=0.78\linewidth]{87}}
\end{center}

\end{document}
